What Happened to The Birth Rate?

### 2022-02-28 outputs/paper/paper.Rmd
Add data source for LGBT related analysis

## Data Source
Part of our data are from the NCHS(National Center for Health Statistics)[@nvss], in particular, we acquired the US birth rate data for the past 40 years, Figure \@ref(fig:fig-past-40-years) shows the US birth rate from 1980 - 2020, as we can see, the birth rate declined significantly after 2007, which is the time of the Great Recession. We also generated data from U.S. Birth Rate 1950-2022[@birthrate]. We selected the top 3 countries that are affected most and least by the Great Recession according to rankings determined by comparing currency devaluations, equity market declines, and rising sovereign bond spreads. These measures tend to track developments in the real economy during times of economic crisis when financial strain handicaps consumption, investment, and in many cases government spending, which limits GDP and employment growth[@rank]. TODO: ADD DATA SOURCE AND BREIFLY TALK ABOUT IT

@@

>>>>

## Data Source
Part of our data are from the NCHS(National Center for Health Statistics)[@nvss], in particular, we acquired the US birth rate data for the past 40 years, Figure \@ref(fig:fig-past-40-years) shows the US birth rate from 1980 - 2020, as we can see, the birth rate declined significantly after 2007, which is the time of the Great Recession. We also generated data from U.S. Birth Rate 1950-2022[@birthrate]. We selected the top 3 countries that are affected most and least by the Great Recession according to rankings determined by comparing currency devaluations, equity market declines, and rising sovereign bond spreads. These measures tend to track developments in the real economy during times of economic crisis when financial strain handicaps consumption, investment, and in many cases government spending, which limits GDP and employment growth[@rank].

The data used to analyze the impact to birth rate brought by LGBT population growth comes from School of Law, UCLA[@will_institute]. The analysis done be School of Law, UCLA[@will_institute] were from the data collected for the Gallup Daily Tracking survey.

The data used to analyze LGBT population trends comes from GALLUP News [@us_lgbt_trend], which is the source of data of the LGBT Demographics analysis. The data is based on telephone interviews conducted in 2020 with a random sample of 15,349 adults (18+), living in the 50 states and the District of Columbia. The entire sample of national adults has a margin of sampling error is $\pm1\%$ at the $95\%$ confidence level. The results based on the total sample of 692 LGBT adults has a sample error of $\pm5\%$ with a $95\%$ confidence level.

@@

The LGBT demographics data spans 2012 to 2017. The sample is a approximately 350,000 U.S. adults (18+) who resides in the 50 states and district of Columbia. The data describes LGBT Data & Demographics such as LGBT proportion of population by States, characteristics of LGBT people (race, gender distribution, etc.), socioeconomic indicators (income, education level, etc.) and State comparison.

The GALLUP News data used to analyze LGBT population trend shows the LGBT population proportion and distribution trend from 2012 to 2020 by year and generation, as well as the distribution of sexual orientation of different gender identity.
